[dcpo_demsupport]

### 2020-08-08 paper/dcpo_demsupport.Rmd
ggarrange version, not ideal

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  plm, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse, # data wrangling
  dotwhisker # visualization
)

@@

```{r polarizationVisualization, eval = FALSE}
# Bootstrap to get confidence intervals

library(boot)

@@

# bootstrapping with 1000 replications 
bootstrapCI_sigma <- function(aData) {
  aSigma <- aData$sigma
  result_temp <- boot(data = aSigma,
                      statistic = Bmean,
                      R = 1000) %>%
    boot.ci(type = "bca")
  tibble(
    mean = mean(aSigma),
    conf.low = result_temp$bca[4],
    conf.high = result_temp$bca[5]
  )
}

@@

dwplot(df_result_dcpo, by_2sd = FALSE) %>% 
  relabel_predictors(
    c(
      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
      `plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)",
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
      #there's a lag in the replication file
      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") +
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank(),
        legend.position = "none")

>>>>

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse, # data wrangling
  dotwhisker # visualization
)

@@

```{r polarizationVisualization, fig.cap="Variance of Polarization"}
# Bootstrap to get confidence intervals----

@@

## bootstrapping with 1000 replications 
bootstrapCI_sigma <- function(aData) {
  aSigma <- aData$sigma
  result_temp <- boot(data = aSigma,
                      statistic = Bmean,
                      R = 1000) %>%
    boot.ci(type = "bca")
  tibble(
    mean = mean(aSigma),
    conf.low = result_temp$bca[4],
    conf.high = result_temp$bca[5]
  )
}

@@

load(here::here("output", "estimates_dcpo.RDS"))
load(here::here("output", "estimates_cls.RDS"))

df_plot <- df_result_cls[[1]] %>% 
  mutate(model = "Uncertainty\n Ignored",
         type = "Pooled OLS")

df_plot <- df_result_dcpo[[1]] %>% 
  mutate(model = "DCPO",
         type = "Pooled OLS") %>% 
  rename(std.error = se) %>% 
  bind_rows(df_plot)

df_plot <- df_result_cls[[3]] %>% 
  mutate(model = "Uncertainty\n Ignored",
         type = "System GMM") %>% 
  bind_rows(df_plot)

df_plot <- df_result_dcpo[[3]] %>% 
  mutate(model = "DCPO",
         type = "System GMM") %>% 
  rename(std.error = se) %>% 
  bind_rows(df_plot) %>% 
  select(term, estimate, std.error, model, type)

## Facet cause NA column, very weird. 
plot_estimate <- map(c("Pooled OLS", "System GMM"), function(aType) {
  filter(df_plot, type == aType) %>%
    dwplot(by_2sd = FALSE) %>%
    relabel_predictors(
      c(
        `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
        `plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
        `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
        `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
        `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
        `plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
        `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
        `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
        `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
        `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
        `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
        `plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
        `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
        `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
        `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
        `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)",
        `plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)"
      )
    ) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle(aType) +
    xlab("Coefficient Estimate") +
    theme(axis.title.y = element_blank())
})

library(ggpubr)
ggarrange(plotlist = plot_estimate, common.legend = TRUE)
